\section{WORK EXPERIENCE}

2022 --- current. \emph{BASTA}\footnote{\url{https://basta.is}}. Co-founder, Technical advisor.\\
2017 --- current. \emph{Gangverk}\footnote{\url{https://gangverk.is}}. CA, COO, Senior Developer, Software Architect, Web Discipline Lead, Team Lead. Working with Sotheby's\footnote{\url{https://www.sothebys.com}} on digital products related to online auctions and e-commerce.\\
2016 --- 2017. \emph{Kolibri}\footnote{\url{https://www.kolibri.is/}}. Senior Developer. Working with \emph{Iceland Travel}\footnote{\url{https://www.icelandtravel.is/}} on e-commerce products.\\
2015 --- 2016. \emph{Plain Vanilla Games}. Senior Developer. Working on various aspects of the trivia game QuizUp and the QuizUp social network.\\
2012 --- 2015. \emph{Gagnavarslan (Azazo)}. Senior Developer. Working on various aspects of CoreData (SaaS document storage system). Data pipelines and data migrations.
2010 --- 2010. \emph{Reykjavík University}\footnote{\url{https://ru.is}}. Graduate students - Independent study. Project: ``Daemonizing and enhancing IceNLP for the purpose of machine translation.''. Supervisor: Dr. Hrafn Loftsson.\\
2009 --- 2012. \emph{Samskip Holding B.V}\footnote{\url{https://samskip.com}}. Software Developer. Working on internal applications and solutions related to BI.\\
2008 --- 2008. (Summer). \emph{Landsbanki Íslands}\footnote{\url{https://www.landsbankinn.is/}}. Software developer.\\
2007 --- 2007 (Summer). \emph{Samskip Holding B.V}. Help desk technician.

