\section{TEACHING}
\textbf{2023 - spring}:
Computer Science B.Sc final projects (T-404-LOKA) at Reykjavik University.
Instructor and examiner in following projects.

\begin{itemize}
\item ``Final Project - Myrkur Games''. Ran. Project collaborator: Myrkur Games. Instructor.

\item ``Fróðleiksfúsi''. Anna Rósa Ásgeirsdóttir, Finnur Eiríksson, Kristín Þórðardóttir, Þórey Ósk Árnadóttir. Project collaborator: Þekkingarsetur Suðurnesja and Jökulá ehf. Instructor.

\item ``Regn - Android app''. Guðjón Guðjónsson, Jakob Óli Bergsveinsson, Sædís Björk Jónsdóttir. Project collaborator: Regn and Kolibri. Inspector.

\item ``Developing a Game from Beginning to End''. Hjörleifur Guðnason, Karl Bachmann Eyrúnarson, Pálína Líf Ingadóttir. Project collaborator: Jóhannes Sigurðsson. Inspector.
\end{itemize}

\textbf{2021 - spring}:
Computer Science B.Sc final projects (T-404-LOKA) at Reykjavik University.
Instructor and examiner in following projects.

\begin{itemize}
\item ``Men\&Mice - Micetro Slack Integration''. Einar Oddur Páll Rúnarsson, Kristján Ari Tómasson, Róbert Elís Villalobos. Project collaborator: Men\&Mice. Instructor.

\item ``Tempo Plugins''. Annija Apine, Davíd Bjarni Bjornsson, Haukur Breki Hilmarsson, Ragnar Geir Ragnarsson. Project collaborator: Tempo. Inspector.
\end{itemize}

\textbf{2020 - spring}:
Computer Science B.Sc final projects (T-404-LOKA) at Reykjavik University.
Instructor and examiner in following projects.

\begin{itemize}
\item ``Golden Gate''. Bryndís Charlotte Sturludóttir, Petra Kristín Frantz.
    Project collaborator: NetApp. Instructor.

\item ``Vitco'. Gunnar Jörgen Viggósson, Haraldur Björnsson. Project collaborator: Videntifier, Moral Sentiments. Inspector.
\end{itemize}

\textbf{2019 - spring}:
Computer Science B.Sc final projects (T-404-LOKA) at Reykjavik University.
Instructor and examiner in following projects.

\begin{itemize}
\item ``Hljóðrit.is''. Hreiðar Ólafur Arnarsson, Héðinn Grétar Hendriksson, Jón
    Ingvar Karlsson Brune. Project collaborator: SFH. Instructor.

\item ``Vessel Monitoring System - Map Implementation''. Ólafur Karl Stefánsson,
	Björn Þórsson. Project collaborator: Trakcwell. Instructor.

\item ``Using SARSA with function approximation to create policies for MCTS''.
	Dagmar Lukka Loftsdóttir, Hera Hjaltadóttir, Valgarður Ragnheiðar Ívarsson.
		Research Bachelor of Science (B.Sc.). Inspector.

\item ``AGR System Monitor''. Arnar Ingi Halldórsson, Jóhann Ívar Björnsson,
    Sveinn Björnsson. collaborator: AGR Dynamics. Inspector.
\end{itemize}

\textbf{2016 - spring}:
Computer Science B.Sc final projects (T-404-LOKA) at Reykjavik University.
Instructor and examiner in following projects.

\begin{itemize}
\item ``Receptor''. Steinunn Marta Friðriksdóttir, Svava Dögg Björgvinsdóttir,
    Sveinbjörn Guðjohnsen. Project collaborator: Applicon. Instructor.

\item ``Launráður - Launagreining skv jafnlaunastaðli''. Einar Logi Hreinsson,
    Pétur Bergmann Halldórsson, Vignir Karl Gylfason. Project collaborator: GBS
        Ráðgjöf. Instructor.

\item ``VR Casual Flyby''. Björgvin Brynjarsson, Björn Ingi Baldvinsson, Daníel
    Jóhannsson, Kristján Ingi Einarsson. Project collaborator: Cosmosis Games.
        Instructor.

\item ``Rauntímaeftirlit með bensínstöðvum''. Arnar Dóri Ásgeirsson, Ásgeir
    Daði Þórisson, Hafþór Snær Þórsson, Sigurður Már Atlason. Project
        collaborator: LS Retail. Examiner.

\item ``User analytics and customer support tools for STARBORNE''. Arnar Kári
    Ágústsson, Árni Benedikt Árnason, Daníel Benediktsson, Jón Freysteinn
        Jónsson, Jörundur Jörundsson. Project collaborator: Solid Clouds.
        Examiner.

\item ``TravAble''. Birgir Þór Óskarsson, Jóhann Gíslason, Þórhildur Guðný
    Sigþórsdóttir. Project collaborator TravAble. Examiner.
\end{itemize}


\textbf{2015 - fall}: Web services (T-514-VEFT). Teacher at Reykjavik
University. Computer Science B.Sc final projects (T-404-LOKA) at Reykjavik
University. Instructor and examiner in following projects.

\begin{itemize}
\item ``Strætó bs. app fyrir Windows 10''. Ásgeir Atlason, Georg Styrmir
    Rúnarsson. Project collaborator: Strætó, Stokkur ehf. Instructor.

\item ``Project Discovery for EVE Online''. Hjalti Leifsson, Jóhann Örn
    Bjarkason. Project collaborator: CCP Games, MMOS sárl og CADIA. Instructor.

\item ``Classy network''. Karítas Ólafsdóttir, Sveinn Dal Björnsson. Project
    collaborator: Jökulá. Inspector.

\item ``Vitinn''. Daníel Agnarsson, Friðrik Valdimarsson. Project collaborator:
    Tollstjóraembættið, SFS, Matís. Inspector.
\end{itemize}


\textbf{2015 - spring}: Computer Science B.Sc final projects (T-404-LOKA) at Reykjavik University. Instructor and examiner in following projects.

\begin{itemize}
\item ``Vegabréfaumsóknir Advania''.
    \url{http://skemman.is/item/view/1946/22165}. Guðmundur Stefánsson, Guðni
        Aðalsteinn Þrastarson. Advania. Project collaborator: Advania.
        Instructor.

\item ``Thrifter''. \url {http://skemman.is/en/item/view/1946/22799}. Ari Freyr
    Ásgeirsson, Ívar Oddsson, Sigursteinn Bjarni Húbertsson, Valgeir Björnsson,
        Ævar Ísak Ástþórsson. Instructor.

\item ``Tempo Mobile''. \url{http://skemman.is/handle/1946/23255}. Árni Fannar
    Þráinsson, Gunnar Smári Agnarsson, Sindri Sigurjónsson, Theodór Tómas
        Theodórsson. Project collaborator: Tempo. Instructor.

\item ``Birdie''. \url{http://skemman.is/handle/1946/22126}. Alexander Baldvin
    Sigurðsson, Arnór Ýmir Guðjónsson, Matthías Sigurðsson. Examiner.

\item ``Stoðkerfi fyrir námsleiki''. \url{http://skemman.is/handle/1946/22139}.
    Anton Hilmarsson, Bergsteinn Karlsson, Hilmar Geir Eiðsson, Jón Helgi
        Jónsson, Jörundur Kristinsson, Sigrún Arna Sigurðardóttir. Project
        collaborator: Costner Games. Examiner.

\item ``Fanaments App''. \url{http://skemman.is/handle/1946/22134}. Davíð
    Hafþór Kristinsson, Natan Örn Ólafsson. Project collaborator: Fanaments.
        Examiner.
\end{itemize}

\textbf{2014 - summer}:
Instructor UROP project at Reykjavik University ((T-622-UROP)), project report
title ``SugerApp - Android application for diabetes''. Evaluated as B.Sc final
project.

Supervisor UROP project at Reykjavik University (T-622-UROP), project report
title ``FocusVer''. Evaluated as B.Sc final project.

\textbf{2014 - fall}: UROP project instructor (T-622-UROP) at Reykjavik
University. Kári Tristan Helgason, Björn Orri Sæmundsson, Starkaður
Hróbjartsson. Report title ``MySchool app for IOS with Swift''.

Supervisor UROP project at Reykjavik University, project report title
``MySchool app for IOS with Swift''.

Web services (T-514-VEFT). Teacher at Reykjavik University. Computer Science
B.Sc final projects (T-404-LOKA) at Reykjavik University. Instructor and
examiner in following projects.

\begin{itemize}
\item ``Case Request On-line''. \url{http://hdl.handle.net/1946/23250}. Jón
    Heiðar Erlendsson, Ragnar Ómarsson. Project collaborator: Annata.
        Instructor.

\item ``Marvin: Deployment system for CoreData''.
    \url{http://skemman.is/handle/1946/23244}. Sigurður Rúnar Helgason, Marinó
        Fannar Pálsson, Gadidjah Margrét Ögmundsdóttir. Project collaborator:
        Azazo. Instructor.

\item ``CESAR - Stundatöflugerðar kerfi fyrir HR''.
    \url{http://skemman.is/handle/1946/23249}. Einar Þór Traustason, Margrét S.
        Kristjánsdóttir. Examiner. 

\item ``Evert''. \url{http://hdl.handle.net/1946/23245}. Hulda Lárusdóttir,
    Hildur Andrjesdóttir, Ólafur Ómarsson. Examiner.
\end{itemize}

\textbf{2014 - spring}:
M.Sc. Thesis Committee. Áslaug Eiríksdóttir (30 ECTS, supervised by Dr. Yngvi
Björnsson), Reykjavik University, June 2014. Thesis title ``The Software
Adoption Process Seen Through System Logs''.

Practical Project (T-205-VERK), instructor in a three week undergraduate
project for Computer Science students -- second semester.

Computer Science B.Sc final projects (T-404-LOKA) at Reykjavik University.
Instructor and examiner in following projects.

\begin{itemize}
\item
``Heilsan mín í raun og veru''. \url{http://skemman.is/handle/1946/21018}.
        Guðleif Harðardóttir, Ingvar Sigurðsson, Jóhannes Gunnar Heiðarsson,
        Jón Atli Baldvinsson, Kristján Broder Lund. Project collaborator: Tm
        Software. Instructor.

\item
``Ársreikningar á netinu''. \url{http://skemman.is/handle/1946/21098}. Carsten
        Petersen, Róbert Gunnarsson, Sigurrós Soffía Kristinsdóttir. Project
        collaborator: Kóði ehf. Instructor. 

\item
``Rental Inspector smáforrit fyrir Windows 8.1''.
        \url{http://hdl.handle.net/1946/21023}. Halldór Vilhjálmsson, Sindri
        Már Sigfússon, Sverrir Snævar Jónsson. Project collaborator: Annata.
        Examiner.

\item
``Leiksýningar á Íslandi''. \url{http://hdl.handle.net/1946/20997}. Eyjólfur
        Kristjánsson, Kristján Guðjónsson, Steindór Grétar Kristinsson. Project
        collaborator: Leikminjasafn Íslands. Examiner.
\end{itemize}


\textbf{2013 - fall}: Computer Graphics (T-511-TGRA), Teacher assistant at
Reykjavik University with Kári Halldórsson. Computer Science B.Sc final
projects (T-404-LOKA) at Reykjavik University. Instructor and examiner in
following projects.

\begin{itemize}
\item ``Gas Teddy Bear Bobo'', \url{http://skemman.is/handle/1946/17247}. Arnar
    Þór Úlfarsson, Björn Heiðar Rúnarsson, Bjarki Dagsson. Project
        collaborator: Entrio ehf. Instructor.

\item ``Minotour''. Project collaborator: TM Software. Instructor.

\item ``Farandlausnir fyrir snjallsíma - Windows''. Project collaborator:
    Unimaze ehf. Examiner.

\item ``Farandlausnir fyrir snjallsíma - Android''. Project collaborator:
    Unimaze ehf. Examiner.
\end{itemize}


\textbf{2013 - spring}: Web Programming (T-213-VEFF), Teacher at Reykjavik
University. Computer Science B.Sc final projects (T-404-LOKA) at Reykjavik
University. Instructor and examiner in following projects.

\begin{itemize}
\item ``mPOS for iOS''. \url{http://skemman.is/handle/1946/16277}. Ragnar
    Jóhannsson, Jón Hilmar Gústafsson. Project collaborator: Handpoint.
        Instructor.

\item ``Námsefnishluti í nemenda/kennaravef Innu'',
    \url{http://skemman.is/handle/1946/16271}. Andri Björn Ólafsson, Björn
        Þorsteinsson, Hlynur Sigurðsson, Kristborg Anna Ámundadóttir, Olga Rún
        Kristjánsdóttir. Project collaborator: Advania. Examiner. 
\end{itemize}


\textbf{2012 - fall}:
Computer Graphics (T-511-TGRA), Teacher assistant at Reykjavík University with
Kári Halldórsson. Computer Science B.Sc final projects (T-404-LOKA) at
Reykjavik University. Instructor and examiner in following projects.

\begin{itemize}
\item `Mótakerfi fyrir Frjálsíþróttasamband Íslands`,
    \url{http://skemman.is/handle/1946/14148}. Magnús Skúlason, Guðni Þór
        Guðnason. Project collaborator: FRÍ. Instructor.

\item ``Leikir.is. Vefsíða fyrir tölvuleiki''.
    \url{http://skemman.is/handle/1946/16819}. Malte Bjarki Mohrmann, Snorri
        Örn Daníelsson, Tryggvi Geir Magnússon. Project collaborator: D3
        Miðlar. Examiner.
\end{itemize}


\textbf{2012 - spring}:
Computer Science B.Sc final projects (T-404-LOKA) at Reykjavik University.
Instructor and examiner in following projects.

\begin{itemize}
\item ``MB-System''. \url{http://skemman.is/en/item/view/1946/14078}. Frans
    Veigar Garðarsson, Finnur Kolbeinsson, Jón Rúnar Arnarsson, Ólína Björg
        Þorsteinsdóttir. Project collaborator: Mentor. Instructor.

\item ``Aerarium'', \url{http://skemman.is/handle/1946/14085}. Axel Axelsson,
    Ásgeir Jónasson, Kristján Oddsson, Óskar Ómarsson. Project collaborator:
        Arion Banki. Instructor.

\item ``Tónlistargagnagrunnurinn - islensktonlist.is'.
    \url{http://skemman.is/handle/1946/15201}. Arnþór Snær Sævarsson, Einar
        Valur Aðalsteinsson, Hilmar Kári Hallbjörnsson. Examiner.

\item ``Litgreining í Android''. Edward Alexander Eiríksson, Jón Friðrik
    Sigurðarson Viðar Friðriksson, Þorsteinn Þorvaldsson. Examiner.
\end{itemize}


\textbf{2011 - fall}
Assistant developer in M.Sc. final project at Reykjavik University. Thesis
title ``A Face Recognition Plug-in for the PhotoCube Browser.''.
\url{http://www.ru.is/media/td-msc-ritgerdir/KristjanRunarssonMSc.pdf}.


\textbf{2011 - spring}:
Computer Science B.Sc final projects (T-404-LOKA) at Reykjavik University.
Instructor and examiner in following projects.

\begin{itemize}
\item ``F-Prot GUI''. \url{http://skemman.is/handle/1946/9147}. Andrés Ævar
    Grétarsson, Þórður Gunnarsson, Gunnar Tómas Gunnarsson, Haukur Jónasson.
        Instructor.

\item ``Marorka Mobile Portal''. \url{http://skemman.is/handle/1946/9135}.
    Einar Þorgeirsson, Bjarni Davíð Guðmundsson, Arnar Ólafsson. Project
        collaborator: Marorka. Instructor.

\item ``Instant Game for Facebook and Mobile''.
    \url{http://skemman.is/handle/1946/9188}. Ásgeir Einarsson, Bergur Páll
        Gylfason, Daði Magnússon, Vignir Jónsson. Project collaborator:
        Betware. Examiner.

\item ``Meðhöndlun viðvarana frá símstöðvum''.
    \url{http://skemman.is/handle/1946/9086}. Davíð Halldór Lúðvíksson,
        Gunnlaugur Sigurðsson. Project collaborator: Síminn. Examiner.
\end{itemize}
